RNA-seq from 4 cell populations

### 2021-07-30 deconvolution/fans4/molec_profiling.Rmd
bug fix

  form = ~ CellType + Gender
  vobj = voomWithDreamWeights(dge, form, infoSub, plot=FALSE, save.plot=TRUE, BPPARAM=SnowParam(12, progressbar=TRUE))

  form = ~ CellType + Gender
  fit = dream( vobj, form, infoSub, BPPARAM=SnowParam(12, progressbar=TRUE))
  fit = eBayes(fit)

@@

  form = ~ CellType + Gender
  vobj = voomWithDreamWeights(dge, form, infoSub, plot=FALSE, save.plot=TRUE, BPPARAM=SnowParam(6, progressbar=TRUE))

@@

    form = ~ CellType
    vobj = voomWithDreamWeights(dge, form, infoSub2, plot=FALSE, save.plot=TRUE, BPPARAM=SnowParam(6, progressbar=TRUE), quiet=TRUE)

    form = ~ CellType
    fit = dream( vobj, form, infoSub2, BPPARAM=SnowParam(6, progressbar=TRUE), quiet=TRUE)
    fit = eBayes(fit)

@@

# Disease
```{r DE.disease}
# Disease
fitDisease = dream( vobj, ~ 0 + CellType*Dx + (1|Individual.ID) + (1|Gender), info, BPPARAM=SnowParam(6, progressbar=TRUE))
```

@@

  key = paste0('CellType', CT, ':DxSCZ')

  if( CT == levels(info$CellType)[1]){
    key = 'DxSCZ'
  }

@@

@@

```{r store, eval=TRUE}
# Code
CODE <- Folder(name = "FANS4 processing and testing", parentId = "syn22231629") # Make sure these match the folder name and parent Id in the first chunk.
CODE <- synStore(CODE)

>>>>

  form = ~ CellType + Gender + Batch
  vobj = voomWithDreamWeights(dge, form, infoSub, plot=FALSE, save.plot=TRUE, BPPARAM=SnowParam(12, progressbar=TRUE))

  form = ~ CellType + Gender + Batch
  fit = dream( vobj, form, infoSub, BPPARAM=SnowParam(12, progressbar=TRUE))
  fit = eBayes(fit)

@@

  form = ~ CellType + Gender + Batch
  vobj = voomWithDreamWeights(dge, form, infoSub, plot=FALSE, save.plot=TRUE, BPPARAM=SnowParam(6, progressbar=TRUE))

@@

    form = ~ CellType + Batch
    vobj = voomWithDreamWeights(dge, form, infoSub2, plot=FALSE, save.plot=TRUE, BPPARAM=SnowParam(6, progressbar=TRUE), quiet=TRUE)

    form = ~ CellType + Batch
    fit = dream( vobj, form, infoSub2, BPPARAM=SnowParam(6, progressbar=TRUE), quiet=TRUE)
    fit = eBayes(fit)

@@

# Disease
```{r DE.disease}
info$I = with(info, paste0(CellType, ".", Dx))

# Disease
form = ~ 0 + I + (1|Individual.ID) + (1|Gender) + (1|Batch)

# contrasts
L = makeContrastsDream(form, info, contrasts=c(
              GABA.Dx = "IGABA.SCZ - IGABA.Control",
              GLU.Dx = "IGLU.SCZ - IGLU.Control",
              MgAs.Dx = "IMgAs.SCZ - IMgAs.Control",
              Olig.Dx = "IOlig.SCZ - IOlig.Control"))

fitDisease = dream( vobj[1:10,], form, info, L=L, BPPARAM=SnowParam(12, progressbar=TRUE))
```

@@

  key = paste0( CT, '.Dx')

@@

```{r, eval=FALSE}
knitr::knit_exit()
```

@@

```{r store, eval=FALSE}
# Code
CODE <- Folder(name = "FANS4 processing and testing", parentId = "syn22231629") # Make sure these match the folder name and parent Id in the first chunk.
CODE <- synStore(CODE)
